\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-21 paper.tex
objectives updated

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{TEDAT}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in s-d pair set}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$d_i=(\mathbf{b_i}, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$ &\multicolumn{6}{|l}{the set of arrived demands and admitted demands}\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\section{$\mathsf{TEDAT}$}\label{HATE}
In this section, we make a full description of $\mathsf{TEDAT}$ framework, which contains three parts, i.e., admission control, traffic scheduling and failure recovery.
Table \ref{Notation} shows the main notations.
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High acceptance ratio and low latency:}  
  Tenants' BA demands might arrive at anytime. 
  The system should be able to accommodate as many BA demands as possible under the constraint of availability and bandwidth targets.
\item \textbf{Maintain high availability:}
The system must make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Handle failures:}
When there are link failures, the system can reroute traffic that would go over failed links over the remaining active tunnels with small revenue loss instead.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{Demands abstraction}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a tenant could be a customer who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify them.
We now present $\mathsf{TEDAT}$ 's availability abstraction, which aims to guarantee the bandwidth-based availability of services.

@@

\section{$\mathsf{TEDAT}$ system} \label{system}
%In this section, we show the design and some implementation details of $\mathsf{TEDAT}$ prototype.
%In this section, we show the design of $\mathsf{TEDAT}$ (Traffic Engineering for Diverse Availability Targets) system, which is able to provide high bandwidth-based availability to services.
%$\mathsf{TEDAT}$ system tries to achieve the following objectives:

>>>>

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{TEDAT}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$ &\multicolumn{6}{|l}{the set of arrived demands and admitted demands}\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\section{The $\mathsf{TEDAT}$ framework}\label{HATE}
In this section, we discuss the details of $\mathsf{TEDAT}$, which contains three parts, i.e., admission control, traffic scheduling and failure recovery, using notations summarized in Table \ref{Notation}. 
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High admission ratio and low admission latency:}  
  Bandwidth availability demands might arrive at anytime. 
  The system should be able to efficiently accommodate as many BA demands as possible under the constraint of network capacity and failure probabilities, as this would increase service agility and bring more revenue. %availability and bandwidth targets.
\item \textbf{High availability for allocated bandwidth:}
The system should be able to optimize its achieved availability in a probabilistic manner, 
as this would, in the long term, reduce potential penalties (i.e., refund due to SLA violations) and retain a good reputation. This can be achieved by making a good match between demands on higher availability and paths with low failure probability.
%make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
%Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Automatic and economical failure recovery:}
If any link failure really happens, the system should reroute traffic away from that link, 
while minimizing any possible collateral damage to normal traffic, i.e., congestion and lower bandwidth availability due to rerouting.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{Abstraction of bandwidth availability demands}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a tenant could be a customer who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify them.
We now present $\mathsf{TEDAT}$ 's availability abstraction, which aims to guarantee the bandwidth-based availability of services.

@@

\section{system implementation} \label{system}
%In this section, we show the design and some implementation details of $\mathsf{TEDAT}$ prototype.
%In this section, we show the design of $\mathsf{TEDAT}$ (Traffic Engineering for Diverse Availability Targets) system, which is able to provide high bandwidth-based availability to services.
%$\mathsf{TEDAT}$ system tries to achieve the following objectives:
